The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
interpret conn redund
interpret layer similarity
refs

output: 
    #word_document
    github_document
---

@@

Sociality exists across scales (Whitehead 2008). For example, grooming and mating relationships require close proximity between conspecifics and occur over brief time periods (e.g. Carter et al. 2015), whereas social association represents shared space use by members of the same social group (Franks et al. 2010). Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges. In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over larger spatial and temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al. 2014; Farine 2015). Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (see Glossary; Farine et al. 2015).

@@

### Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
* Degree deviation: deviation of degree across layers. High degree deviation = large difference between degree for an individual across layers. Low degree deviation = individuals are similarly connected across layers. 
* Graph strength: weighted version of degree. High graph strength = highly connected. Not summed in this case across layers. 
* Neighbors: number of unique individuals adjacent to each actor. Considered in a single layer, this is equal to the degree. 
* Neighborhood: number of unique individuals across all layers. High neighborhood = a high number of unique individuals connected to an actor. 
* Relevance: layer centric metric, corresponding to the number of neighbors on a layer divided by the total neighborhood for each actor. High relevance means that the layer is highly relevant to the individuals connections. A low relevance means this layer does not contribute many neighbors to an individuals overall neighborhood. 
* Connective redundancy: the total multilayer neighborhood divided by the multidegree. High connective redundancy indicates a multilayer network that has many repeated edges across layers between an actor and its neighbours. Low connective redundancy is

@@

Animal movement undoubtedly affects the social environment (Strandburg-Peshkin et al. 2015), and multilayer networks are no exception (Mourier et al. 2019). Movement is a dynamic process that is related to the resources an individual consumes within their home range and their general space use (Van Moorter et al. 2016). Collective movement can reduce group-level predation via detection-dilution trade-offs and improve information transfer about the quality or location of resources to other group members (Jolles et al. 2019). Social processes, movement decisions, and space use are therefore inextricably linked.

>>>>

output: 
    #word_document
    github_document

references: ../references/franks.bib
---

@@

Sociality exists across scales (Whitehead 2008). For example, grooming and mating relationships require close proximity between conspecifics and occur over brief time periods (e.g. Carter et al. 2015), whereas social association represents shared space use by members of the same social group [@Franks2010]. Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges. In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over larger spatial and temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al. 2014; Farine 2015). Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (see Glossary; Farine et al. 2015).

@@

### Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
* Degree deviation: deviation of degree across layers. High degree deviation = large difference between degree for an individual across layers. Low degree deviation = individuals are similarly connected across layers. 
* Graph strength: weighted version of degree. High graph strength = highly connected. Not summed in this case across layers. 
* Neighbors: number of unique individuals adjacent to each actor. Considered in a single layer, this is equal to the degree. 
* Neighborhood: number of unique individuals across all layers. High neighborhood = a high number of unique individuals connected to an actor. 
* Relevance: layer centric metric, corresponding to the number of neighbors on a layer divided by the total neighborhood for each actor. High relevance means that the layer is highly relevant to the individuals connections. A low relevance means this layer does not contribute many neighbors to an individuals overall neighborhood. 
* Connective redundancy: the total multilayer neighborhood divided by the multidegree. High connective redundancy indicates a multilayer network that has many repeated edges across layers between an actor and its neighbours. Low connective redundancy indicates that each layer is important for preserving all social ties. 
* Layer similarily/correlation: how similar each layer is (Brodka 2018). right now - standard deviation of the vectors.. so decrease deviation = increased similarity

@@

Animal movement undoubtedly affects an individual's social environment (Strandburg-Peshkin et al. 2015), and multilayer networks are no exception (Mourier et al. 2019). Movement is a dynamic process that is related to the resources an individual consumes within their home range and their general space use (Van Moorter et al. 2016). Collective movement can reduce group-level predation via detection-dilution trade-offs and improve information transfer about the quality or location of resources to other group members (Jolles et al. 2019). Social processes, movement decisions, and space use are therefore inextricably linked.
